---
title: "IPBES Data Unit"
format:
  html:
    toc: false
---

```{r}
#| echo: false
#| warning: false
#| message: false

library(gh)

assessment_pages_base <- "https://ipbes-data.github.io/IPBES_Assessment_Directories"
tg_directory_page <- "https://ipbes-data.github.io/IPBES_TG_Directory/"
shinyapps_account <- Sys.getenv("SHINYAPPS_ACCOUNT", unset = "ipbes-data")

assessments <- read.csv(file.path("input", "assessments.csv"), stringsAsFactors = FALSE)
dir_map <- read.csv(file.path("input", "assessment_directory_map.csv"), stringsAsFactors = FALSE)
tg_labels_fallback <- read.csv(file.path("input", "technical_guideline_labels.csv"), stringsAsFactors = FALSE)
shiny_apps_fallback <- read.csv(file.path("input", "shiny_apps_fallback.csv"), stringsAsFactors = FALSE)

assessments[] <- lapply(assessments, function(x) if (is.character(x)) trimws(x) else x)
dir_map[] <- lapply(dir_map, function(x) if (is.character(x)) trimws(x) else x)
tg_labels_fallback[] <- lapply(tg_labels_fallback, function(x) if (is.character(x)) trimws(x) else x)
shiny_apps_fallback[] <- lapply(shiny_apps_fallback, function(x) if (is.character(x)) trimws(x) else x)

dir_map <- dir_map[
  !is.na(dir_map$abbreviation) & nzchar(dir_map$abbreviation) &
    !is.na(dir_map$directory_path) & nzchar(dir_map$directory_path),
  ,
  drop = FALSE
]

tg_labels_fallback <- tg_labels_fallback[
  !is.na(tg_labels_fallback$repo_name) & nzchar(tg_labels_fallback$repo_name) &
    !is.na(tg_labels_fallback$title) & nzchar(tg_labels_fallback$title) &
    !is.na(tg_labels_fallback$page_url) & nzchar(tg_labels_fallback$page_url),
  ,
  drop = FALSE
]

empty_shiny_apps <- function() {
  data.frame(name = character(0), title = character(0), url = character(0), status = character(0), stringsAsFactors = FALSE)
}

empty_repos <- function() {
  data.frame(repo_name = character(0), repo_url = character(0), stringsAsFactors = FALSE)
}

empty_tg_labels <- function() {
  data.frame(repo_name = character(0), title = character(0), page_url = character(0), stringsAsFactors = FALSE)
}

get_cached_repos <- function(path = "tree.rds") {
  if (!file.exists(path) || !requireNamespace("data.tree", quietly = TRUE)) {
    return(empty_repos())
  }

  repo_tree <- tryCatch(readRDS(path), error = function(e) NULL)
  if (is.null(repo_tree)) {
    return(empty_repos())
  }

  repo_df <- tryCatch(
    data.tree::ToDataFrameTree(repo_tree, "repoName", "url"),
    error = function(e) NULL
  )
  if (is.null(repo_df) || nrow(repo_df) == 0) {
    return(empty_repos())
  }

  repo_df <- repo_df[
    !is.na(repo_df$repoName) & !is.na(repo_df$url) &
      nzchar(repo_df$repoName) & nzchar(repo_df$url),
    ,
    drop = FALSE
  ]

  unique(data.frame(
    repo_name = repo_df$repoName,
    repo_url = repo_df$url,
    stringsAsFactors = FALSE
  ))
}

get_org_repos <- function(org = "IPBES-Data") {
  repos_raw <- tryCatch(
    gh("GET /orgs/:org/repos", org = org, per_page = 200),
    error = function(e) NULL
  )

  if (!is.null(repos_raw) && length(repos_raw) > 0) {
    repos_live <- data.frame(
      repo_name = vapply(repos_raw, function(x) x$name, character(1)),
      repo_url = vapply(repos_raw, function(x) x$html_url, character(1)),
      stringsAsFactors = FALSE
    )
    return(list(data = repos_live, source = "live"))
  }

  repos_cached <- get_cached_repos()
  if (nrow(repos_cached) > 0) {
    return(list(data = repos_cached, source = "cached"))
  }

  list(data = empty_repos(), source = "none")
}

escape_html <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;", x, fixed = TRUE)
  x <- gsub(">", "&gt;", x, fixed = TRUE)
  x <- gsub('"', "&quot;", x, fixed = TRUE)
  x <- gsub("'", "&#39;", x, fixed = TRUE)
  x
}

get_assessment_directory_path <- function(abbreviation, map_df) {
  hit <- which(tolower(map_df$abbreviation) == tolower(abbreviation))
  if (length(hit) == 0) {
    return("")
  }
  map_df$directory_path[hit[1]]
}

build_assessment_directory_link_html <- function(abbreviation, map_df, base_url) {
  directory_path <- get_assessment_directory_path(abbreviation, map_df)

  if (!nzchar(directory_path)) {
    return("<span class='assessment-repos-empty'>No published directory.</span>")
  }

  full_url <- paste0(base_url, "/", directory_path, "/index.html")
  paste0(
    "<a href='", escape_html(full_url), "' target='_blank' rel='noopener'>",
    "IPBES_Assessment_Directories/", escape_html(directory_path), "/index.html",
    "</a>"
  )
}

normalize_url <- function(url) {
  if (is.na(url) || !nzchar(url)) {
    return("")
  }

  if (grepl("^https?://", url)) {
    return(url)
  }

  if (startsWith(url, "/")) {
    return(paste0("https://ipbes-data.github.io", url))
  }

  paste0("https://ipbes-data.github.io/", url)
}

extract_repo_name_from_url <- function(url) {
  cleaned <- sub("/+$", "", url)
  parts <- strsplit(cleaned, "/", fixed = TRUE)[[1]]
  if (length(parts) == 0) {
    return("")
  }
  tail(parts, 1)
}

order_tg_labels <- function(df) {
  if (nrow(df) == 0) {
    return(df)
  }

  non_template <- !(
    grepl("TEMPLATE", df$repo_name, ignore.case = TRUE) |
      grepl("^\\s*TEMPLATE\\b", df$title, ignore.case = TRUE)
  )
  df <- df[non_template, , drop = FALSE]

  if (nrow(df) == 0) {
    return(df)
  }

  match <- regexec("^\\s*Part\\s*([0-9]+)\\s*([A-Za-z]?)\\b", df$title, ignore.case = TRUE)
  parsed <- regmatches(df$title, match)

  sort_group <- rep(1L, nrow(df))
  sort_num <- rep(9999L, nrow(df))
  sort_suffix <- rep(999L, nrow(df))

  for (i in seq_len(nrow(df))) {
    p <- parsed[[i]]
    if (length(p) >= 2) {
      sort_group[i] <- 0L
      sort_num[i] <- suppressWarnings(as.integer(p[2]))
      suffix <- if (length(p) >= 3) toupper(p[3]) else ""
      sort_suffix[i] <- if (nzchar(suffix)) match(suffix, LETTERS) else 0L
      if (is.na(sort_suffix[i])) {
        sort_suffix[i] <- 999L
      }
    }
  }

  df <- unique(df)
  df <- df[order(sort_group, sort_num, sort_suffix, tolower(df$title)), , drop = FALSE]
  df
}

get_tg_labels_from_site <- function(directory_url = tg_directory_page) {
  if (!requireNamespace("rvest", quietly = TRUE)) {
    return(empty_tg_labels())
  }

  page <- tryCatch(rvest::read_html(directory_url), error = function(e) NULL)
  if (is.null(page)) {
    return(empty_tg_labels())
  }

  anchors <- rvest::html_elements(page, "a")
  href <- rvest::html_attr(anchors, "href")
  title <- trimws(rvest::html_text2(anchors))

  href <- vapply(href, normalize_url, character(1))
  repo_name <- vapply(href, extract_repo_name_from_url, character(1))

  out <- data.frame(
    repo_name = repo_name,
    title = title,
    page_url = href,
    stringsAsFactors = FALSE
  )

  out <- out[
    grepl("^IPBES_TG_", out$repo_name) & nzchar(out$title) & nzchar(out$page_url),
    ,
    drop = FALSE
  ]

  if (nrow(out) == 0) {
    return(empty_tg_labels())
  }

  order_tg_labels(out)
}

load_tg_labels <- function(fallback_df) {
  live <- get_tg_labels_from_site()
  if (nrow(live) > 0) {
    return(list(data = live, source = "live website"))
  }

  if (nrow(fallback_df) > 0) {
    return(list(data = order_tg_labels(fallback_df), source = "fallback csv"))
  }

  list(data = empty_tg_labels(), source = "none")
}

sanitize_shiny_apps <- function(df) {
  if (is.null(df) || nrow(df) == 0) {
    return(empty_shiny_apps())
  }

  pick_col <- function(x, candidates, fallback = "") {
    hit <- candidates[candidates %in% names(x)]
    if (length(hit) == 0) {
      return(rep(fallback, nrow(x)))
    }
    out <- x[[hit[1]]]
    if (is.null(out)) {
      return(rep(fallback, nrow(x)))
    }
    out
  }

  app_name <- pick_col(df, c("name", "application_name", "app_name"))
  app_title <- pick_col(df, c("title", "display_name", "name", "application_name"))
  app_url <- pick_col(df, c("url", "application_url", "app_url"))
  app_status <- pick_col(df, c("status", "application_status", "state"))

  out <- data.frame(
    name = app_name,
    title = app_title,
    url = app_url,
    status = app_status,
    stringsAsFactors = FALSE
  )

  out[] <- lapply(out, function(x) if (is.character(x)) trimws(x) else x)
  out$title <- ifelse(is.na(out$title) | !nzchar(out$title), out$name, out$title)
  out$status <- ifelse(is.na(out$status), "", out$status)

  out <- out[!is.na(out$url) & nzchar(out$url), , drop = FALSE]
  if (nrow(out) == 0) {
    return(empty_shiny_apps())
  }

  out <- unique(out)
  out[order(tolower(out$title), tolower(out$name)), , drop = FALSE]
}

get_shiny_apps_from_api <- function(account_name = shinyapps_account) {
  if (!requireNamespace("rsconnect", quietly = TRUE)) {
    return(empty_shiny_apps())
  }

  token <- Sys.getenv("SHINYAPPS_TOKEN", unset = "")
  secret <- Sys.getenv("SHINYAPPS_SECRET", unset = "")
  if (!nzchar(token) || !nzchar(secret)) {
    return(empty_shiny_apps())
  }

  connected <- tryCatch({
    rsconnect::setAccountInfo(
      name = account_name,
      token = token,
      secret = secret,
      server = "shinyapps.io"
    )
    TRUE
  }, error = function(e) FALSE)

  if (!connected) {
    return(empty_shiny_apps())
  }

  apps_raw <- tryCatch(
    rsconnect::applications(account = account_name, server = "shinyapps.io"),
    error = function(e) NULL
  )

  sanitize_shiny_apps(apps_raw)
}

load_shiny_apps <- function(fallback_df, account_name = shinyapps_account) {
  live <- get_shiny_apps_from_api(account_name = account_name)
  if (nrow(live) > 0) {
    return(list(data = live, source = "shinyapps api"))
  }

  fallback <- sanitize_shiny_apps(fallback_df)
  if (nrow(fallback) > 0) {
    return(list(data = fallback, source = "fallback csv"))
  }

  list(data = empty_shiny_apps(), source = "none")
}

repo_result <- get_org_repos()
org_repos <- repo_result$data
repo_source <- repo_result$source

tg_result <- load_tg_labels(tg_labels_fallback)
tg_pages <- tg_result$data
tg_source <- tg_result$source

shiny_result <- load_shiny_apps(shiny_apps_fallback, account_name = shinyapps_account)
shiny_apps <- shiny_result$data
shiny_source <- shiny_result$source

if (nrow(org_repos) > 0 && nrow(tg_pages) > 0) {
  tg_repo_names <- org_repos$repo_name[grepl("^IPBES_TG_", org_repos$repo_name)]
  tg_pages <- tg_pages[tg_pages$repo_name %in% tg_repo_names, , drop = FALSE]
  tg_pages <- order_tg_labels(tg_pages)
}

n_assessments <- nrow(assessments)
n_tg_repos <- nrow(tg_pages)
n_shiny_apps <- nrow(shiny_apps)
```

::: {.hero-panel}
::: {.hero-copy}
{{< include content/home/hero.md >}}
:::

::: {.hero-metrics}
::: {.metric-card}
<p class="metric-value">`r n_assessments`</p>
<p class="metric-label">Assessment Streams</p>
:::
::: {.metric-card}
<p class="metric-value">`r n_tg_repos`</p>
<p class="metric-label">Technical Guideline Pages</p>
:::
::: {.metric-card}
<p class="metric-value">`r n_shiny_apps`</p>
<p class="metric-label">Published Shiny Apps</p>
:::
:::
:::

## What You Can Do Here

{{< include content/home/features.md >}}

## Assessment Explorer {#assessment-explorer}

{{< include content/home/explorer_intro.md >}}

::: {.search-wrap}
<label for="assessment-filter">Find an assessment</label>
<input id="assessment-filter" type="search" placeholder="Try: Nexus, IAS, Transformative..." autocomplete="off">
<p id="assessment-count" class="search-count"></p>
<p id="assessment-empty" class="search-empty" hidden>No assessment matches your search.</p>
:::

::: {.assessment-grid #assessment-grid}
```{r}
#| echo: false
#| results: asis

for (i in seq_len(nrow(assessments))) {
  row <- assessments[i, ]
  search_blob <- tolower(paste(row$full_name, row$short_name, row$abbreviation))
  directory_link <- build_assessment_directory_link_html(row$abbreviation, dir_map, assessment_pages_base)

  cat(
    paste0(
      "<article class='assessment-card' data-search='", escape_html(search_blob), "'>",
      "<p class='assessment-title'>", escape_html(row$short_name), "</p>",
      "<p>", escape_html(row$full_name), "</p>",
      "<span class='assessment-tag'>", escape_html(row$abbreviation), "</span>",
      "<p class='assessment-repos'><span>Assessment directory:</span> ",
      directory_link,
      "</p>",
      "</article>"
    )
  )
}
```
:::

## Technical Guidelines {#technical-guidelines}

Technical guideline titles are taken from the published TG Directory page (source: `r tg_source`).

::: {.search-wrap}
<label for="tg-filter">Find a technical guideline</label>
<input id="tg-filter" type="search" placeholder="Try: Part 3, Colour, Zenodo..." autocomplete="off">
<p id="tg-count" class="search-count"></p>
<p id="tg-empty" class="search-empty" hidden>No technical guideline matches your search.</p>
:::

::: {.tg-grid}
```{r}
#| echo: false
#| results: asis

if (nrow(tg_pages) == 0) {
  cat("<p class='tg-empty'>No technical guideline pages found.</p>")
} else {
  for (i in seq_len(nrow(tg_pages))) {
    row <- tg_pages[i, ]
    search_blob <- tolower(paste(row$title, row$repo_name))
    cat(
      paste0(
        "<article class='tg-card' data-search='", escape_html(search_blob), "'>",
        "<a href='", escape_html(row$page_url), "' target='_blank' rel='noopener'>",
        escape_html(row$title),
        "</a>",
        "</article>"
      )
    )
  }
}
```
:::

## Shiny Apps

Published apps for account `r shinyapps_account` (source: `r shiny_source`).

::: {.search-wrap}
<label for="app-filter">Find a Shiny app</label>
<input id="app-filter" type="search" placeholder="Try: dashboard, indicator, explorer..." autocomplete="off">
<p id="app-count" class="search-count"></p>
<p id="app-empty" class="search-empty" hidden>No Shiny app matches your search.</p>
:::

::: {.app-grid}
```{r}
#| echo: false
#| results: asis

if (nrow(shiny_apps) == 0) {
  cat("<p class='tg-empty'>No Shiny apps found.</p>")
} else {
  for (i in seq_len(nrow(shiny_apps))) {
    row <- shiny_apps[i, ]
    search_blob <- tolower(paste(row$title, row$name, row$status))
    status_html <- if (nzchar(row$status)) {
      paste0("<p class='app-status'>Status: ", escape_html(row$status), "</p>")
    } else {
      ""
    }
    cat(
      paste0(
        "<article class='app-card' data-search='", escape_html(search_blob), "'>",
        "<a href='", escape_html(row$url), "' target='_blank' rel='noopener'>",
        escape_html(row$title),
        "</a>",
        status_html,
        "</article>"
      )
    )
  }
}
```
:::

<script>
document.addEventListener("DOMContentLoaded", function () {
  function wireFilter(inputId, cardSelector, countId, emptyId) {
    const input = document.getElementById(inputId);
    const cards = Array.from(document.querySelectorAll(cardSelector));
    const count = document.getElementById(countId);
    const empty = document.getElementById(emptyId);

    if (!input || cards.length === 0) return;

    function applyFilter() {
      const query = input.value.trim().toLowerCase();
      let visible = 0;

      cards.forEach(function (card) {
        const haystack = card.dataset.search || "";
        const show = query === "" || haystack.includes(query);
        card.classList.toggle("is-hidden", !show);
        if (show) visible += 1;
      });

      count.textContent = visible + (visible === 1 ? " result" : " results");
      empty.hidden = visible !== 0;
    }

    input.addEventListener("input", applyFilter);
    applyFilter();
  }

  wireFilter("assessment-filter", ".assessment-card", "assessment-count", "assessment-empty");
  wireFilter("tg-filter", ".tg-card", "tg-count", "tg-empty");
  wireFilter("app-filter", ".app-card", "app-count", "app-empty");
});
</script>
