---
title: "IPBES Data Unit"
format:
  html:
    toc: false
---

```{r}
#| echo: false
#| warning: false
#| message: false

source("scripts/site_data_utils.R")

assessment_pages_base <- "https://ipbes-data.github.io/IPBES_Assessment_Directories"
tg_directory_page <- "https://ipbes-data.github.io/IPBES_TG_Directory/"
shinyapps_account <- Sys.getenv("SHINYAPPS_ACCOUNT", unset = "ipbes-data")

inputs <- load_site_inputs()
assessments <- inputs$assessments
dir_map <- inputs$dir_map
tg_labels_fallback <- inputs$tg_labels_fallback
shiny_apps_fallback <- inputs$shiny_apps_fallback

repo_result <- get_org_repos_for_index(org = "IPBES-Data")
org_repos <- repo_result$data
repo_source <- repo_result$source

tg_result <- load_tg_labels(tg_labels_fallback, directory_url = tg_directory_page)
tg_pages <- tg_result$data
tg_source <- tg_result$source

shiny_result <- load_shiny_apps(shiny_apps_fallback, account_name = shinyapps_account)
shiny_apps <- shiny_result$data
shiny_source <- shiny_result$source

if (nrow(org_repos) > 0 && nrow(tg_pages) > 0) {
  tg_repo_names <- org_repos$repo_name[grepl("^IPBES_TG_", org_repos$repo_name)]
  tg_pages <- tg_pages[tg_pages$repo_name %in% tg_repo_names, , drop = FALSE]
  tg_pages <- order_tg_labels(tg_pages)
}

n_assessments <- nrow(assessments)
n_tg_repos <- nrow(tg_pages)
n_shiny_apps <- nrow(shiny_apps)
```

::: {.hero-panel}
::: {.hero-copy}
{{< include content/home/hero.md >}}
:::

::: {.hero-metrics}
::: {.metric-card}
<p class="metric-value">`r n_assessments`</p>
<p class="metric-label">Assessment Streams</p>
:::
::: {.metric-card}
<p class="metric-value">`r n_tg_repos`</p>
<p class="metric-label">Technical Guideline Pages</p>
:::
::: {.metric-card}
<p class="metric-value">`r n_shiny_apps`</p>
<p class="metric-label">Published Shiny Apps</p>
:::
:::
:::

## What You Can Do Here

{{< include content/home/features.md >}}

## Assessment Explorer {#assessment-explorer}

{{< include content/home/explorer_intro.md >}}

::: {.search-wrap}
<label for="assessment-filter">Find an assessment</label>
<input id="assessment-filter" type="search" placeholder="Try: Nexus, IAS, Transformative..." autocomplete="off">
<p id="assessment-count" class="search-count"></p>
<p id="assessment-empty" class="search-empty" hidden>No assessment matches your search.</p>
:::

::: {.assessment-grid #assessment-grid}
```{r}
#| echo: false
#| results: asis

for (i in seq_len(nrow(assessments))) {
  row <- assessments[i, ]
  search_blob <- tolower(paste(row$full_name, row$short_name, row$abbreviation))
  directory_link <- build_assessment_directory_link_html(row$abbreviation, dir_map, assessment_pages_base)

  cat(
    paste0(
      "<article class='assessment-card' data-search='", escape_html(search_blob), "'>",
      "<p class='assessment-title'>", escape_html(row$short_name), "</p>",
      "<p>", escape_html(row$full_name), "</p>",
      "<span class='assessment-tag'>", escape_html(row$abbreviation), "</span>",
      "<p class='assessment-repos'><span>Assessment directory:</span> ",
      directory_link,
      "</p>",
      "</article>"
    )
  )
}
```
:::

## Technical Guidelines {#technical-guidelines}

Technical guideline titles are taken from the published TG Directory page (source: `r tg_source`).

::: {.search-wrap}
<label for="tg-filter">Find a technical guideline</label>
<input id="tg-filter" type="search" placeholder="Try: Part 3, Colour, Zenodo..." autocomplete="off">
<p id="tg-count" class="search-count"></p>
<p id="tg-empty" class="search-empty" hidden>No technical guideline matches your search.</p>
:::

::: {.tg-grid}
```{r}
#| echo: false
#| results: asis

if (nrow(tg_pages) == 0) {
  cat("<p class='tg-empty'>No technical guideline pages found.</p>")
} else {
  for (i in seq_len(nrow(tg_pages))) {
    row <- tg_pages[i, ]
    search_blob <- tolower(paste(row$title, row$repo_name))
    cat(
      paste0(
        "<article class='tg-card' data-search='", escape_html(search_blob), "'>",
        "<a href='", escape_html(row$page_url), "' target='_blank' rel='noopener'>",
        escape_html(row$title),
        "</a>",
        "</article>"
      )
    )
  }
}
```
:::

## Shiny Apps

Published apps for account `r shinyapps_account` (source: `r shiny_source`).

::: {.search-wrap}
<label for="app-filter">Find a Shiny app</label>
<input id="app-filter" type="search" placeholder="Try: dashboard, indicator, explorer..." autocomplete="off">
<p id="app-count" class="search-count"></p>
<p id="app-empty" class="search-empty" hidden>No Shiny app matches your search.</p>
:::

::: {.app-grid}
```{r}
#| echo: false
#| results: asis

if (nrow(shiny_apps) == 0) {
  cat("<p class='tg-empty'>No Shiny apps found.</p>")
} else {
  for (i in seq_len(nrow(shiny_apps))) {
    row <- shiny_apps[i, ]
    search_blob <- tolower(paste(row$title, row$name, row$status))
    status_html <- if (nzchar(row$status)) {
      paste0("<p class='app-status'>Status: ", escape_html(row$status), "</p>")
    } else {
      ""
    }
    cat(
      paste0(
        "<article class='app-card' data-search='", escape_html(search_blob), "'>",
        "<a href='", escape_html(row$url), "' target='_blank' rel='noopener'>",
        escape_html(row$title),
        "</a>",
        status_html,
        "</article>"
      )
    )
  }
}
```
:::

<script>
document.addEventListener("DOMContentLoaded", function () {
  function wireFilter(inputId, cardSelector, countId, emptyId) {
    const input = document.getElementById(inputId);
    const cards = Array.from(document.querySelectorAll(cardSelector));
    const count = document.getElementById(countId);
    const empty = document.getElementById(emptyId);

    if (!input || cards.length === 0) return;

    function applyFilter() {
      const query = input.value.trim().toLowerCase();
      let visible = 0;

      cards.forEach(function (card) {
        const haystack = card.dataset.search || "";
        const show = query === "" || haystack.includes(query);
        card.classList.toggle("is-hidden", !show);
        if (show) visible += 1;
      });

      count.textContent = visible + (visible === 1 ? " result" : " results");
      empty.hidden = visible !== 0;
    }

    input.addEventListener("input", applyFilter);
    applyFilter();
  }

  wireFilter("assessment-filter", ".assessment-card", "assessment-count", "assessment-empty");
  wireFilter("tg-filter", ".tg-card", "tg-count", "tg-empty");
  wireFilter("app-filter", ".app-card", "app-count", "app-empty");
});
</script>
