---
title: "Repository List"
format:
  html:
    toc: true
    toc-depth: 2
execute:
  echo: false
  warning: false
  message: false
---

This document lists repositories in the [IPBES-Data GitHub organization](https://github.com/IPBES-Data).

Assessment directory links point to published pages under [IPBES_Assessment_Directories](https://ipbes-data.github.io/IPBES_Assessment_Directories/), with paths configured in `input/assessment_directory_map.csv`.

```{r}
library(knitr)
source("scripts/site_data_utils.R")

assessment_pages_base <- "https://ipbes-data.github.io/IPBES_Assessment_Directories"
tg_directory_page <- "https://ipbes-data.github.io/IPBES_TG_Directory/"
shinyapps_account <- Sys.getenv("SHINYAPPS_ACCOUNT", unset = "ipbes-data")

inputs <- load_site_inputs()
assessments <- inputs$assessments
dir_map <- inputs$dir_map
tg_labels_fallback <- inputs$tg_labels_fallback
shiny_apps_fallback <- inputs$shiny_apps_fallback

repo_result <- get_org_repos_for_repos(org = "IPBES-Data")
repos <- repo_result$data
repo_source <- repo_result$source

tg_result <- load_tg_labels(tg_labels_fallback, directory_url = tg_directory_page)
tg_pages <- tg_result$data
tg_source <- tg_result$source

shiny_result <- load_shiny_apps(shiny_apps_fallback, account_name = shinyapps_account)
shiny_apps <- shiny_result$data
shiny_source <- shiny_result$source

if (nrow(repos) > 0 && nrow(tg_pages) > 0) {
  tg_repo_names <- repos$repo_name[grepl("^IPBES_TG_", repos$repo_name)]
  tg_pages <- tg_pages[tg_pages$repo_name %in% tg_repo_names, , drop = FALSE]
  tg_pages <- order_tg_labels(tg_pages)
}
```

## Assessment Directories

Repository source for dynamic lists: `r repo_source`.

```{r}
directory_paths <- vapply(
  assessments$abbreviation,
  get_assessment_directory_path,
  character(1),
  map_df = dir_map
)

assessment_dirs <- data.frame(
  Assessment = assessments$short_name,
  Abbreviation = assessments$abbreviation,
  `Directory path` = directory_paths,
  `Assessment directory` = vapply(
    directory_paths,
    format_assessment_dir_link,
    character(1),
    base_url = assessment_pages_base
  ),
  stringsAsFactors = FALSE
)

kable(assessment_dirs, escape = FALSE)
```

## Technical Guidelines

Names and links are taken from the published TG Directory page (source: `r tg_source`).

```{r}
if (nrow(tg_pages) == 0) {
  cat("No technical guideline pages found.")
} else {
  tg_table <- data.frame(
    `Technical guideline` = paste0("<a href='", tg_pages$page_url, "' target='_blank' rel='noopener'>", tg_pages$title, "</a>"),
    stringsAsFactors = FALSE
  )
  kable(tg_table, escape = FALSE)
}
```

## Shiny Apps

Apps are queried dynamically from account `r shinyapps_account` (source: `r shiny_source`).

```{r}
if (nrow(shiny_apps) == 0) {
  cat("No Shiny apps found.")
} else {
  apps_table <- data.frame(
    `App` = paste0("<a href='", shiny_apps$url, "' target='_blank' rel='noopener'>", shiny_apps$title, "</a>"),
    `Status` = ifelse(nzchar(shiny_apps$status), shiny_apps$status, ""),
    stringsAsFactors = FALSE
  )
  kable(apps_table, escape = FALSE)
}
```

## All Repositories

```{r}
if (nrow(repos) == 0) {
  cat("Repository data is currently unavailable from the GitHub API.")
} else {
  repos <- repos[order(tolower(repos$repo_name)), , drop = FALSE]
  repos$Repository <- paste0("<a href='", repos$url, "' target='_blank' rel='noopener'>", repos$repo_name, "</a>")
  repos$Description <- repos$description

  repo_table <- repos[, c("Repository", "Description")]
  kable(repo_table, escape = FALSE)
}
```
