---
title: "Repository List"
format:
  html:
    toc: true
    toc-depth: 2
execute:
  echo: false
  warning: false
  message: false
---

This document lists repositories in the [IPBES-Data GitHub organization](https://github.com/IPBES-Data).

Assessment directory links point to published pages under [IPBES_Assessment_Directories](https://ipbes-data.github.io/IPBES_Assessment_Directories/), with paths configured in `input/assessment_directory_map.csv`.

```{r}
library(gh)
library(knitr)

assessment_pages_base <- "https://ipbes-data.github.io/IPBES_Assessment_Directories"
tg_directory_page <- "https://ipbes-data.github.io/IPBES_TG_Directory/"
shinyapps_account <- Sys.getenv("SHINYAPPS_ACCOUNT", unset = "ipbes-data")

empty_repos <- function() {
  data.frame(repo_name = character(0), description = character(0), url = character(0), stringsAsFactors = FALSE)
}

empty_tg_labels <- function() {
  data.frame(repo_name = character(0), title = character(0), page_url = character(0), stringsAsFactors = FALSE)
}

empty_shiny_apps <- function() {
  data.frame(name = character(0), title = character(0), url = character(0), status = character(0), stringsAsFactors = FALSE)
}

get_cached_repos <- function(path = "tree.rds") {
  if (!file.exists(path) || !requireNamespace("data.tree", quietly = TRUE)) {
    return(empty_repos())
  }

  repo_tree <- tryCatch(readRDS(path), error = function(e) NULL)
  if (is.null(repo_tree)) {
    return(empty_repos())
  }

  repo_df <- tryCatch(
    data.tree::ToDataFrameTree(repo_tree, "repoName", "url", "description"),
    error = function(e) NULL
  )
  if (is.null(repo_df) || nrow(repo_df) == 0) {
    return(empty_repos())
  }

  repo_df <- repo_df[
    !is.na(repo_df$repoName) & !is.na(repo_df$url) &
      nzchar(repo_df$repoName) & nzchar(repo_df$url),
    ,
    drop = FALSE
  ]

  unique(data.frame(
    repo_name = repo_df$repoName,
    description = ifelse(is.na(repo_df$description), "", repo_df$description),
    url = repo_df$url,
    stringsAsFactors = FALSE
  ))
}

repos_raw <- tryCatch(
  gh("GET /orgs/:org/repos", org = "IPBES-Data", per_page = 200),
  error = function(e) list()
)

if (length(repos_raw) == 0) {
  repos <- get_cached_repos()
  repo_source <- if (nrow(repos) > 0) "cached (tree.rds)" else "unavailable"
} else {
  repos <- data.frame(
    repo_name = vapply(repos_raw, function(x) x$name, character(1)),
    description = vapply(repos_raw, function(x) ifelse(is.null(x$description), "", x$description), character(1)),
    url = vapply(repos_raw, function(x) x$html_url, character(1)),
    stringsAsFactors = FALSE
  )
  repo_source <- "live GitHub API"
}

assessments <- read.csv(file.path("input", "assessments.csv"), stringsAsFactors = FALSE)
dir_map <- read.csv(file.path("input", "assessment_directory_map.csv"), stringsAsFactors = FALSE)
tg_labels_fallback <- read.csv(file.path("input", "technical_guideline_labels.csv"), stringsAsFactors = FALSE)
shiny_apps_fallback <- read.csv(file.path("input", "shiny_apps_fallback.csv"), stringsAsFactors = FALSE)

assessments[] <- lapply(assessments, function(x) if (is.character(x)) trimws(x) else x)
dir_map[] <- lapply(dir_map, function(x) if (is.character(x)) trimws(x) else x)
tg_labels_fallback[] <- lapply(tg_labels_fallback, function(x) if (is.character(x)) trimws(x) else x)
shiny_apps_fallback[] <- lapply(shiny_apps_fallback, function(x) if (is.character(x)) trimws(x) else x)

dir_map <- dir_map[
  !is.na(dir_map$abbreviation) & nzchar(dir_map$abbreviation) &
    !is.na(dir_map$directory_path) & nzchar(dir_map$directory_path),
  ,
  drop = FALSE
]

tg_labels_fallback <- tg_labels_fallback[
  !is.na(tg_labels_fallback$repo_name) & nzchar(tg_labels_fallback$repo_name) &
    !is.na(tg_labels_fallback$title) & nzchar(tg_labels_fallback$title) &
    !is.na(tg_labels_fallback$page_url) & nzchar(tg_labels_fallback$page_url),
  ,
  drop = FALSE
]

get_assessment_directory_path <- function(abbreviation) {
  hit <- which(tolower(dir_map$abbreviation) == tolower(abbreviation))
  if (length(hit) == 0) {
    return("")
  }
  dir_map$directory_path[hit[1]]
}

format_assessment_dir_link <- function(directory_path) {
  if (!nzchar(directory_path)) {
    return("No published directory")
  }

  paste0(
    "<a href='", assessment_pages_base, "/", directory_path, "/index.html",
    "' target='_blank' rel='noopener'>IPBES_Assessment_Directories/", directory_path, "/index.html</a>"
  )
}

normalize_url <- function(url) {
  if (is.na(url) || !nzchar(url)) {
    return("")
  }

  if (grepl("^https?://", url)) {
    return(url)
  }

  if (startsWith(url, "/")) {
    return(paste0("https://ipbes-data.github.io", url))
  }

  paste0("https://ipbes-data.github.io/", url)
}

extract_repo_name_from_url <- function(url) {
  cleaned <- sub("/+$", "", url)
  parts <- strsplit(cleaned, "/", fixed = TRUE)[[1]]
  if (length(parts) == 0) {
    return("")
  }
  tail(parts, 1)
}

order_tg_labels <- function(df) {
  if (nrow(df) == 0) {
    return(df)
  }

  non_template <- !(
    grepl("TEMPLATE", df$repo_name, ignore.case = TRUE) |
      grepl("^\\s*TEMPLATE\\b", df$title, ignore.case = TRUE)
  )
  df <- df[non_template, , drop = FALSE]

  if (nrow(df) == 0) {
    return(df)
  }

  match <- regexec("^\\s*Part\\s*([0-9]+)\\s*([A-Za-z]?)\\b", df$title, ignore.case = TRUE)
  parsed <- regmatches(df$title, match)

  sort_group <- rep(1L, nrow(df))
  sort_num <- rep(9999L, nrow(df))
  sort_suffix <- rep(999L, nrow(df))

  for (i in seq_len(nrow(df))) {
    p <- parsed[[i]]
    if (length(p) >= 2) {
      sort_group[i] <- 0L
      sort_num[i] <- suppressWarnings(as.integer(p[2]))
      suffix <- if (length(p) >= 3) toupper(p[3]) else ""
      sort_suffix[i] <- if (nzchar(suffix)) match(suffix, LETTERS) else 0L
      if (is.na(sort_suffix[i])) {
        sort_suffix[i] <- 999L
      }
    }
  }

  df <- unique(df)
  df <- df[order(sort_group, sort_num, sort_suffix, tolower(df$title)), , drop = FALSE]
  df
}

get_tg_labels_from_site <- function(directory_url = tg_directory_page) {
  if (!requireNamespace("rvest", quietly = TRUE)) {
    return(empty_tg_labels())
  }

  page <- tryCatch(rvest::read_html(directory_url), error = function(e) NULL)
  if (is.null(page)) {
    return(empty_tg_labels())
  }

  anchors <- rvest::html_elements(page, "a")
  href <- rvest::html_attr(anchors, "href")
  title <- trimws(rvest::html_text2(anchors))

  href <- vapply(href, normalize_url, character(1))
  repo_name <- vapply(href, extract_repo_name_from_url, character(1))

  out <- data.frame(
    repo_name = repo_name,
    title = title,
    page_url = href,
    stringsAsFactors = FALSE
  )

  out <- out[
    grepl("^IPBES_TG_", out$repo_name) & nzchar(out$title) & nzchar(out$page_url),
    ,
    drop = FALSE
  ]

  if (nrow(out) == 0) {
    return(empty_tg_labels())
  }

  order_tg_labels(out)
}

load_tg_labels <- function(fallback_df) {
  live <- get_tg_labels_from_site()
  if (nrow(live) > 0) {
    return(list(data = live, source = "live website"))
  }

  if (nrow(fallback_df) > 0) {
    return(list(data = order_tg_labels(fallback_df), source = "fallback csv"))
  }

  list(data = empty_tg_labels(), source = "none")
}

sanitize_shiny_apps <- function(df) {
  if (is.null(df) || nrow(df) == 0) {
    return(empty_shiny_apps())
  }

  pick_col <- function(x, candidates, fallback = "") {
    hit <- candidates[candidates %in% names(x)]
    if (length(hit) == 0) {
      return(rep(fallback, nrow(x)))
    }
    out <- x[[hit[1]]]
    if (is.null(out)) {
      return(rep(fallback, nrow(x)))
    }
    out
  }

  app_name <- pick_col(df, c("name", "application_name", "app_name"))
  app_title <- pick_col(df, c("title", "display_name", "name", "application_name"))
  app_url <- pick_col(df, c("url", "application_url", "app_url"))
  app_status <- pick_col(df, c("status", "application_status", "state"))

  out <- data.frame(
    name = app_name,
    title = app_title,
    url = app_url,
    status = app_status,
    stringsAsFactors = FALSE
  )

  out[] <- lapply(out, function(x) if (is.character(x)) trimws(x) else x)
  out$title <- ifelse(is.na(out$title) | !nzchar(out$title), out$name, out$title)
  out$status <- ifelse(is.na(out$status), "", out$status)

  out <- out[!is.na(out$url) & nzchar(out$url), , drop = FALSE]
  if (nrow(out) == 0) {
    return(empty_shiny_apps())
  }

  out <- unique(out)
  out[order(tolower(out$title), tolower(out$name)), , drop = FALSE]
}

get_shiny_apps_from_api <- function(account_name = shinyapps_account) {
  if (!requireNamespace("rsconnect", quietly = TRUE)) {
    return(empty_shiny_apps())
  }

  token <- Sys.getenv("SHINYAPPS_TOKEN", unset = "")
  secret <- Sys.getenv("SHINYAPPS_SECRET", unset = "")
  if (!nzchar(token) || !nzchar(secret)) {
    return(empty_shiny_apps())
  }

  connected <- tryCatch({
    rsconnect::setAccountInfo(
      name = account_name,
      token = token,
      secret = secret,
      server = "shinyapps.io"
    )
    TRUE
  }, error = function(e) FALSE)

  if (!connected) {
    return(empty_shiny_apps())
  }

  apps_raw <- tryCatch(
    rsconnect::applications(account = account_name, server = "shinyapps.io"),
    error = function(e) NULL
  )

  sanitize_shiny_apps(apps_raw)
}

load_shiny_apps <- function(fallback_df, account_name = shinyapps_account) {
  live <- get_shiny_apps_from_api(account_name = account_name)
  if (nrow(live) > 0) {
    return(list(data = live, source = "shinyapps api"))
  }

  fallback <- sanitize_shiny_apps(fallback_df)
  if (nrow(fallback) > 0) {
    return(list(data = fallback, source = "fallback csv"))
  }

  list(data = empty_shiny_apps(), source = "none")
}

tg_result <- load_tg_labels(tg_labels_fallback)
tg_pages <- tg_result$data
tg_source <- tg_result$source

shiny_result <- load_shiny_apps(shiny_apps_fallback, account_name = shinyapps_account)
shiny_apps <- shiny_result$data
shiny_source <- shiny_result$source

if (nrow(repos) > 0 && nrow(tg_pages) > 0) {
  tg_repo_names <- repos$repo_name[grepl("^IPBES_TG_", repos$repo_name)]
  tg_pages <- tg_pages[tg_pages$repo_name %in% tg_repo_names, , drop = FALSE]
  tg_pages <- order_tg_labels(tg_pages)
}
```

## Assessment Directories

Repository source for dynamic lists: `r repo_source`.

```{r}
assessment_dirs <- data.frame(
  Assessment = assessments$short_name,
  Abbreviation = assessments$abbreviation,
  `Directory path` = vapply(assessments$abbreviation, get_assessment_directory_path, character(1)),
  `Assessment directory` = vapply(assessments$abbreviation, function(x) {
    format_assessment_dir_link(get_assessment_directory_path(x))
  }, character(1)),
  stringsAsFactors = FALSE
)

kable(assessment_dirs, escape = FALSE)
```

## Technical Guidelines

Names and links are taken from the published TG Directory page (source: `r tg_source`).

```{r}
if (nrow(tg_pages) == 0) {
  cat("No technical guideline pages found.")
} else {
  tg_table <- data.frame(
    `Technical guideline` = paste0("<a href='", tg_pages$page_url, "' target='_blank' rel='noopener'>", tg_pages$title, "</a>"),
    stringsAsFactors = FALSE
  )
  kable(tg_table, escape = FALSE)
}
```

## Shiny Apps

Apps are queried dynamically from account `r shinyapps_account` (source: `r shiny_source`).

```{r}
if (nrow(shiny_apps) == 0) {
  cat("No Shiny apps found.")
} else {
  apps_table <- data.frame(
    `App` = paste0("<a href='", shiny_apps$url, "' target='_blank' rel='noopener'>", shiny_apps$title, "</a>"),
    `Status` = ifelse(nzchar(shiny_apps$status), shiny_apps$status, ""),
    stringsAsFactors = FALSE
  )
  kable(apps_table, escape = FALSE)
}
```

## All Repositories

```{r}
if (nrow(repos) == 0) {
  cat("Repository data is currently unavailable from the GitHub API.")
} else {
  repos <- repos[order(tolower(repos$repo_name)), , drop = FALSE]
  repos$Repository <- paste0("<a href='", repos$url, "' target='_blank' rel='noopener'>", repos$repo_name, "</a>")
  repos$Description <- repos$description

  repo_table <- repos[, c("Repository", "Description")]
  kable(repo_table, escape = FALSE)
}
```
